Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-06 ms.tex
test
no test
Starting on conclusions.

A more readily addressable test is whether a steady-state accretion
picture is capable of explaining the large scatter of typically 2-3
orders of magnitude in the observed distribution of $L_{X}/L_{\rm
  edd}$ at fixed $M_{\bullet}$.  Scatter is expected to result from at
least two effects: (1) the strong sensitivity of the accretion rate
to the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in
combination with the significant dependence of $v_w$ on stochastic
intermittency in the star formation history (Fig.~NICK) (2) The
scatter introduced in using scaling relationships ($\Mbh-\sigma$) 
and ($\Mbh-L_{\rm bulge}$) to measure $\Mbh$ as \citet{Miller+2015} do.  The
combination of (1) and (2) is capable of explaining much of the
observed sample, especially considering that scatter in $L_{\rm X}$
due to variations in $\dot{M}$ is exacerbated by the expectation that
$\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows. At a
wind heating parameter there is an order of magnitude difference between
$\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$
(Fig.~\ref{fig:bh_growth}) which could also lead to scatter of $\dot{M}$ due
to the variation in the Nuker stellar density profile $\Gamma$ at
fixed $M_{\bullet}$. However, the \citet{Pellegrini10} find that the
scatter in $L_X$ is similar if one just looks at core/cusp galaxies separately.

{\bf
  AG Challenge: Scatter in $L_X$ is similar for cores and cusps in Perllegrini}.

@@

  We have calculated steady-state models for circumnuclear medium of a
  sample of early type galaxies, assuming that gas is supplied
  entirely by stellar wind mass loss and heated by shocked stellar
  winds and SNe Ia. We may use these profiles to calculate an $\Mdot$
  onto each of sample galaxy's SMBH, and get the scaling of $\Mdot$
  with $\Mbh$. We may then compare our results with observed trends of
  nuclear x-ray luminosity. Our main conclusions may be summarized as
  follows.

  \begin{enumerate}
  %Younger population=>higher accretion rate; generally higher eta and
  %lower vw except for very young stellar populations.
  \item We find that $\eddr \propto \Mbh^{\alpha}$, where the value of
    $\alpha$ depends on the slope of the stellar density profile
    ($\alpha\simeq0.5,1$ for cusp and core galaxies
    respectively). {\bf AG-these explanations are prehistoric and need
      to be modified. Actually this entire summary needs to be
      revamped, but this can wait until we are closer to completion.}
    One possible solution that the wind mass loss rate (i.e. $\eta$)
    increases with $\Mbh$, as would be expected if low mass SMBH
    preferentially hosted younger stellar populations. Another
    possible explanation is that the effective heating rate of the CNM
    $v_{w}$ decreases with decreasing SMBH mass. This could again be
    due to an older stellar population, since $v_{w} \propto
    \eta^{−1/2}$ for heating sources such as SN Ia and millisecond
    pulsars.
  \item We compare the $\Mdot$ for each of our solution to the one
    calculated from the Bondi formula. We find that they generally to
    a factor of a few. In our model the accretion rate is determined
    from the gas properties at the stagnation radius, $\rs$, which
    agrees with the Bondi radius, $\rb$, within a factor of a
    few. Thus, use of the Bondi formula is a good approximation.
  \item We compare our solutions for density and temperature to those
    inferred from Chandra x-ray observations by \citet{AllenDunn+:2006a}
    and \citet{RussellMcNamara+:2013a} for a handful of galaxies in
    which our sample overlap with theirs. In general, we cannot match
    the observed gas density slope on large scales. 
  \end{enumerate}

>>>>

A more readily addressable test is whether a steady-state accretion
picture is capable of explaining the large scatter of typically 2-3
orders of magnitude in the observed distribution of $L_{X}/L_{\rm
  edd}$ at fixed $M_{\bullet}$.  Scatter is expected to result from at
least two effects: (1) the strong sensitivity of the accretion rate to
the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in
combination with the significant dependence of $v_w$ on stochastic
intermittency in the star formation history (~\ref{fig:NickPlot2}) and
(2) angular momentum of the infalling gas and consequentiallly the
size of small scale outflows may vary from galaxy to galaxy at fixed
$\Mbh$. The combination of (1) and (2) is capable of explaining much
of the observed sample, especially considering that scatter in $L_{\rm
  X}$ due to variations in $\dot{M}$ is exacerbated by the expectation
that $\epsilon_{X} \propto \dot{M}$ for radiatively inefficient
flows. At a wind heating parameter there is an order of magnitude
difference between $\dot{M}$ for core and cusp galaxies at fixed $v_w$
and $M_{\bullet}$ (Fig.~\ref{fig:bh_growth}) which could also lead to
scatter of $\dot{M}$ due to the variation in the Nuker stellar density
profile $\Gamma$ at fixed $M_{\bullet}$. However, \citet{Pellegrini10}
find that the scatter in $L_X$ is similar if one just looks at
core/cusp galaxies separately. There could also be scatter introduced
in using scaling relationships ($\Mbh-\sigma$) and ($\Mbh-L_{\rm
  bulge}$) to measure $\Mbh$ as \citet{Miller+2015} do.

@@

We have calculated steady-state models for circumnuclear medium of
early type galaxies, assuming that gas is supplied entirely by stellar
wind mass loss and heated by shocked stellar winds, supernovae and
black hole feedback. We may use these profiles to calculate an $\Mdot$
onto each of sample galaxy's SMBH, and get the scaling of $\Mdot$ with
$\Mbh$. We may then compare our results with observed trends of
nuclear x-ray luminosity. Our main conclusions may be summarized as
follows.

  \begin{enumerate}
  %Younger population=>higher accretion rate; generally higher eta and
  %lower vw except for very young stellar populations.
  \item We find that $\eddr \propto \Mbh^{\alpha}$ for
    $\Mbh\gsim4\times10^6$ and $\Mbh\lsim 2\times 10^8$, where the
    value of $\alpha$ with $\alpha\simeq$ for galaxies following the
    average star formation histories measured in cosmological
    simulations \citep{MosterNaab+:2013a}. This is in tension
    observations of nuclear X-ray luminosity which suggest that
    $\eddr$ increases towards smaller $\Mbh$
    \citep{Miller+15}. However, it is important to note that the
    inflow rate on large scale (which we calculate) may differ from
    the actual accretion rate as outflows could occur on small
    scales. The outflow rate would depend on the angular momentum of
    the infalling gas and thus the angular momentum of stars in the
    nucleus. The in turn would vary systematically with $\Mbh$.
  \item We expect within scatter in nuclear x-ray luminosities at
    fixed $\Mbh$ from (1) stochastic variation in star formation
    history from galay to galaxy (2) Variations in small scale outflow
    rates due to variations between galactic nuclear angular momenta.
    These variations alone could explain much of the 2-4 orders of
    magnitude of scatter of nuclear x-ray luminosity at fixed $\Mbh$ 
    in the samples of \citet{Miller+15} and \citet{Pellegrini:2010a}.

    Alternatively 
  \item We compare the $\Mdot$ for each of our solution to the one
    calculated from the Bondi formula. We find that they generally to
    a factor of a few. In our model the accretion rate is determined
    from the gas properties at the stagnation radius, $\rs$, which
    agrees with the Bondi radius, $\rb$, within a factor of a
    few. Thus, use of the Bondi formula is a good approximation.
  \end{enumerate}
